Visual Interrogation of Attention-Based Models for Natural Language Inference and Machine Comprehension

### 2018-05-31 EMNLP-demo-paper/result.tex
fix
use BIDAF instead of bidrectional attention flow

\section{Applications}
We demonstrate the proposed visualization system on the decomposable attention network~\cite{parikh2016emnlp}
for the NLI task and the bi-directional attention flow network~\cite{Seo2016} for the MC task.

@@

The user can explore the robustness of the model by examining how the prediction varies when the question is perturbed.
%
As illustrated in ($b1$, and $b2$), the perturbation removes the word ``partial'' in the original sentence, which leads the model to produce a different yet correct answer (``No''). Refer back to ($a1$), we can see the word ``No'' exhibits the second highest probability for the original question.
%
The user can also manually edit the text. As shown in ($b3$). The model still produces the correct answer when changing the question from ``how many'' to ``which''.
%One possible explanation is the word ``Two'' has much higher \emph{att2} attention value compare to ``9'', which may contribute to the current outcome.

>>>>

\section{Applications}
We demonstrate the proposed visualization system on the decomposable attention network~\cite{parikh2016emnlp}
for the NLI task and the BIDAF model~\cite{Seo2016} for the MC task.

@@

The user can explore the robustness of the model by examining how the prediction varies when the question is perturbed.
%
As illustrated in ($b1$, and $b2$), the perturbation removes the word ``partial'' in the original sentence, which leads the model to produce a different yet correct answer (``No''). Referring back to ($a1$), we can see the word ``No'' exhibits the second highest probability for the original question.
%
The user can also manually edit the text. As shown in ($b3$). The model still produces the correct answer when changing the question from ``how many'' to ``which''.
%One possible explanation is the word ``Two'' has much higher \emph{att2} attention value compare to ``9'', which may contribute to the current outcome.
